Modelos

### 2019-01-21 20190117_modelos.Rmd
SUNDAY02
Update 20190117_modelos.Rmd
SUNDAY02

```{r datos, message=FALSE, warning=FALSE, include=FALSE}
rm(list=ls())
load("trump2019.Rdata")
# st <- st %>% na.omit
st$jus2 <- (st$JW2+st$JW3+st$JW4+st$JW4)/4
```

>>>>

```{r datos, message=FALSE, warning=FALSE, include=FALSE}
rm(list=ls())
load("trump2019.Rdata")
# st <- st %>% na.omit
st$jus2 <- (st$JW2+st$JW3+st$JW4+st$JW4)/4 #BJW scale 
```
